Privacy-Preserving Localisation Using Private Linear-Combination Aggregation

### 2020-11-13 main.tex
Removed acknowledgement section as it's not required
Grammarly comma removed

\subsection{Leakage} \label{subsec:leakage}
With the algorithm defined, we can analyse the localisation leakage when the strictly defined LCAO leakage is taken into account. We recall the assumptions on participant capabilities made in Section \ref{subsec:capabilities}. Global and consistent broadcasting is in line with the LCAO definition and required to guarantee the scheme's leakage. Honest-but-curious sensors are not required for scheme privacy, but avoid the possibility of malicious sensors gaining knowledge about other sensors' measurements, when navigator behaviour is dependant on its estimate. This may be achievable by detecting changes in measurements after reporting false ones. As misbehaving sensors are also a known problem which complicates homomorphic operations, active malicious sensors are not considered in the scope of this work.

@@

% use section* for acknowledgment
\section*{Acknowledgment}

Partially supported by ZIM \dots

>>>>

\subsection{Leakage} \label{subsec:leakage}
With the algorithm defined, we can analyse the localisation leakage when the strictly defined LCAO leakage is taken into account. We recall the assumptions on participant capabilities made in Section \ref{subsec:capabilities}. Global and consistent broadcasting is in line with the LCAO definition and required to guarantee the scheme's leakage. Honest-but-curious sensors are not required for scheme privacy, but avoid the possibility of malicious sensors gaining knowledge about other sensors' measurements when navigator behaviour is dependant on its estimate. This may be achievable by detecting changes in measurements after reporting false ones. As misbehaving sensors are also a known problem which complicates homomorphic operations, active malicious sensors are not considered in the scope of this work.

@@
